%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\color{text1}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

% \name{Zheng Rui} % Your name
% \address{Hong Kong University of Science and Technology, Hong Kong} % Your secondary addess (optional)
% \address{(00852)~$\cdot$~5343~$\cdot$~5857 \\ rzhengphy@gmail.com} % Your phone number and email
% \address{http://zhengrui.github.io} % Your address

\begin{document}

\vspace{-10mm}
% \begin{textblock*}{100mm}(.85\textwidth,-4cm)
    % \rotatebox{310}{\colorbox{red!30}{\hspace{50pt}\color{headings}\bf \fontspec[Variant = 2]{Zapfino} Curriculum {Vit\fontspec[Variant = 3]{Zapfino}\ae\hspace{50pt}}}}
% \end{textblock*}

{\centering
    \colorbox{white} {
        \hspace{0.5cm}
        \color{black}\RaisedText{\fontsize{1.5cm}{1.1cm}\selectfont Zheng Rui} % Your name
        % \color{black}\RaisedText{\Huge\bf \fontspec[Variant = 2]{Zapfino} Zheng Rui} % Your name
    }
\hfill
\colorbox{shade}{\textcolor{text1}{
\begin{tabular}{c|p{7cm}}
    \raisebox{-1pt}{\textifsymbol{18}} & {\fontsize{1em}{1em}\selectfont 370 Jay Street, Brooklyn, New York} \\ % Address
\raisebox{-1pt}{\Mobilefone} & +1 9175628187 \\ % Phone number
\raisebox{-1pt}{\Letter} & \href{mailto:rzhengphy@gmail.com}{rzhengphy@gmail.com} \\ % Email address
\Mundus & \href{http://zhengrui.github.io}{http://zhengrui.github.io}\\ % Website
\faGithub & \href{http://github.com/zhengrui}{http://github.com/zhengrui}\\
\faLinkedin & \href{http://hk.linkedin.com/in/rzhenguniq}{http://hk.linkedin.com/in/rzhenguniq}
\end{tabular}
}}\\[15pt]
}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{About}
I currently work as the Principal Research Scientist at Markable. I have a mixed background of physics and computer science. In 2012 I received PhD in physics through researching quantum phase transitions using Monte Carlo algorithms. In 2016 I got MPhil degree in computer science and my thesis is about building a customizable visual privacy protection system for photo sharing. After graduation, I joined Markable as a reserach scientist to develop commercial fashion recognition system. I have worked on several problems from quantum model simulation, network analysis, cloud computing to computer vision and deep learning. I enjoy implementing ideas and debugging systems.

\end{rSection}

\begin{rSection}{Education}

{\bf Hong Kong University of Science and Technology, Hong Kong} \hfill {\bf 2013 - 2016} \\
\hspace*{2em}{\it Thesis: Context-aware visual privacy control} \\
\hspace*{2em}M.Phil. in Computer Science and Engineering

{\bf Institute of Physics, Chinese Academy of Sciences, Beijing} \hfill {\bf 2006 - 2012} \\
\hspace*{2em}{\it Thesis: Monte Carlo methods and applications on magnetic models} \\
\hspace*{2em}Ph.D. in Computational Physics

{\bf Huazhong University of Science and Technology, Wuhan} \hfill {\bf 2002 - 2006} \\
\hspace*{2em}{\it Thesis: Colossal magnetoresistance in Perovskite Oxide} \\
\hspace*{2em}B.S. in Applied Physics

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{MARKABLE. Inc.}{New York}{Principal Research Scientist}{Nov 2017 - Present}{Senior Research Engineer}{Oct 2016 - Nov 2017}
\item Research on learning discriminative feature representions for image search and recommendation of fashion items. Improve the top-2 recall on internal dataset from 12\% to 71\%. The training algorithms have achieved comparable performances on serveral open-sourced fashion datasets. The trained models are serving multiple clients on production. Write patents on image and video retrieval algorithms.
\item Bridge research with deployment. Wrap inference pipelines as modules and dockerize them to ease the integration of research models and algorithms into production, which speeds up the catalog indexing stage significantly.
\item Build the data stack. Participate in the full data loop, from writing specifications, data scraping to data cleaning, visualization and analysis. Write the database module that enables research team to easily pull clean training data.
\item Guide research team to make progresses on several problems from detection, segmentation to tracking. Recruit for research and data team. Supervise interns to explore promising directions and algorithms.
\item Skills: {\it PyTorch, Pandas, Python, Javascript, Caffe, Dask, Flask, Node, React, Qt, D3.js, Docker, Kubernetes, etc.}
\end{rSubsection}

\begin{rSubsection}{Hong Kong University of Science and Technology}{Hong Kong}{Research / Teaching Assistant}{Aug 2013 - Oct 2016}{}{}
\item Lead development in multiple research projects, including {\it OCR on Google Glass}, {\it Mean First Passage Time and Cover Time of random walks on different graphs}, {\it Context-aware visual privacy control}. Deploy state-of-the-art deep learning models on mobile for tasks including scene classification, face recognition, gesture recognition.
\item Develop multiple tools and libraries, including group discussion website, image annotation tool, mobile streaming multiplexing / demultiplexing tool, face alignment library on Android, Caffe mobile library on Android.
\item Administration of lab servers. Provide consultancies for other projects on problems related to machine / deep learning, computer vision and Linux.
\item Teaching assistant of Courses {\it Operating System}, {\it Python Bridging Course}, {\it Social Network Analysis}.
\item Skills: {\it C++, Python, Java, Android, Bash, Linux, Caffe, Torch7, Matlab, Flask, \TeX.}
\end{rSubsection}

\begin{rSubsection}{Beijing Zhong Ruan Co.}{Beijing}{Back End Developer}{Apr 2013 - Aug 2013}{}{}
\item Develop a web based monitoring system for nuclear power plants in Shandong province.
\item Set up development environment for the team and lead back end development.
\item Skills: {\it Spring, Struts, Hibernate, JSP, Javascript, Html, CSS.}
\end{rSubsection}

\begin{rSubsection}{ENIN Tech. Inc.}{Beijing}{R\&D Engineer}{Aug 2012 - Oct 2012}{}{}
\item Design data reconciliation and flow optimization algorithms.
\item Skills: {\it GAMS, linear optimization.}
\end{rSubsection}

\begin{rSubsection}{Institute of Physics, Chinese Academy of Sciences}{Beijing}{Research Assistant}{Sep 2006 - Jun 2012}{}{}
\item Design and implement algorithms for the study of phase transitions in both classical and quantum magnetic models. Focused on Monte Carlo methods and density matrix renormalization group based methods.
\item First principle calculations of band structure and magnetic properties of half-metal materials.
\item Skills: {\it Fortran, C++, Matlab, Python, ALPS, \TeX, Linux.}
\end{rSubsection}

\end{rSection}


\begin{rSection}{Publications}

% \begin{itemize}[leftmargin=*] % no indentation
\begin{itemize}[label=\raisebox{0.25ex}{\tiny\JackStarBold}]
\item Jiayu Shu, Sokol Kosta, Rui Zheng and Pan Hui, \emph{Talk2Me: A Framework for Device-to-Device Augmented Reality Social Network}, \textsf{PerCom 2018 full paper and best demo award}.

\item Dimitris Chatzopoulos, Carlos Bermejo, Zhanpeng Huang, Arailym Butabayeva, Rui Zheng, Morteza Golkarifard and Pan Hui, \emph{Hyperion: A Wearable Augmented Reality System for Text Extraction and Manipulation in the Air}, \textsf{Proceedings of the 8th ACM on Multimedia Systems Conference}, 284-295 (2017).

\item Tongfeng Weng, Jie Zhang, Michael Small, Rui zheng, and Pan Hui, \emph{Memory and betweenness preference in temporal networks induced from time series}, \textsf{Scientific Reports} \underline{7}, 41951 (2017).

\item Jiayu Shu, Rui Zheng and Pan Hui, \emph{Your Privacy Is in Your Hand: Interactive Visual Privacy Control with Tags and Gestures}, \textsf{International Conference on Communication Systems and Networks}, 24-43 (2017).

\item Suren Kumar and Rui Zheng, \emph{Hierarchical Category Detector for Clothing Recognition From Visual Data}, \textsf{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (Workshop)}, 2306-2312 (2017).

\item Tongfeng Weng, Jie Zhang, Moein Khajehnejad, Michael Small, Rui zheng, and Pan Hui, \emph{Navigation by anomalous random walks on complex networks}, \textsf{Scientific Reports} \underline{6}, 37547 (2017). % \href{https://github.com/ZhengRui/mean-first-passage}{Code}.

\item Jiayu Shu, Rui Zheng and Pan Hui, \emph{Cardea: Context-Aware Visual Privacy Protection from Pervasive Cameras}, \textsf{arXiv: 1610.00889}.% \href{https://arxiv.org/abs/1610.00889}{\textsf{arXiv: 1610.00889}}.

\item Jiayu Shu, Rui Zheng and Pan Hui, \emph{Interactive Visual Privacy Control with Gestures}, \textsf{Proceedings of the 14th Annual International Conference on Mobile Systems, Applications, and Services Companion (Demo)}, 120-120 (2016).% \href{https://github.com/ZhengRui/mobisys16demo}{Code}.

\item Carlos Bermejo, Rui Zheng and Pan Hui, \emph{An empirical study of human altruistic behaviors in opportunistic networks}, \textsf{Proceedings of the 7th International Workshop on Hot Topics in Planet-scale mObile computing and online Social neTworking}, 43-48 (2015).% \href{http://bit.ly/2e9Icla}{PDF}.

\item Zheng Rui and Liu Bang-Gui, \emph{Stable two-dimensional ferromagnets made of regular single-layered lattices of single-molecule nanomagnets with perpendicular anisotropy}, \textsf{J. Appl. Phys.} \underline{106}, 054316 (2009).% \href{http://bit.ly/29aBRQD}{PDF}.

\item Zheng Rui and Liu Bang-Gui, \emph{Quantum Monte Carlo study of the phase transition for a generalized Two-Dimensional Staggered Dimerized Heisenberg Model}, \textsf{Chin. Phys. B.} \underline{21}, 116401 (2012).% \href{http://bit.ly/29aBDJb}{PDF}.

\end{itemize}

\end{rSection}

% \begin{rSection}{Patents}
% \begin{itemize}[label=\raisebox{0.25ex}{\tiny\JackStarBold}]
% \item image search
% \item video pipeline
% \end{itemize}
% \end{rSection}

\begin{rSection}{Computer Skills}

\begin{tabular}{ @{\hspace{2.0em}} >{\bfseries}l @{\hspace{6ex}} l }
OS & Ubuntu, OSX, CentOS, Android\\
Languages & C++, Python, Bash, Javascript, Java, Matlab, Lua, Fortran, SQL\\
Tools & \TeX, Vim, WingIDE, Android Studio, Xcode, Inkscape, Omnigraffle\\
Libs & OpenCV, PyTorch, Caffe, Torch7, TensorFlow\\
Frameworks & Flask, React, Node
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Projects}

% \begin{rSubsection}{Side Projects}{}{}{}{}{}

% \item {\bf\em Cardea} - A context aware privacy control system which can enhance users' visual privacy based on their context specific privacy settings. Context includes location, surrounding scene and people. Users can also temporarily overwrite their settings using gestures. \href{https://github.com/ZhengRui/cardea}{Code}.

% \item {\bf\em Caffe Mobile Lib} - An extension from \href{https://github.com/sh1r0/caffe-android-lib}{Caffe-android-lib}, now supports running multiple deep neural networks in Android and batch feature extraction. \href{https://github.com/ZhengRui/caffe-android-lib}{Code}.

% \item {\bf\em Android Face Alignment Lib} - A JNI library which enables android phones to not only detect faces, but also detect facial landmarks and thus do face alignment. \href{https://github.com/ZhengRui/FaceAlignmentJNI}{Code}.

% \item {\bf\em Annota} - Two versions: one is a Flask Web App and another is a PyQt App. Both enable users to annotate images. The annotated images can be used to train detection models. \href{https://github.com/ZhengRui/ImgAnnotaWeb}{Flask App Code}, \href{https://github.com/ZhengRui/ImgAnnotaPyQt4}{Qt App Code}.

% \item {\bf\em Grp-Meeting} - A Flask App which supports publishing contents and posting comments with Markdown syntax. Math symbols are well rendered both in contents and comments thus it is helpful for inner research group discussion. \href{https://github.com/ZhengRui/grpmeeting}{Code}.

% \item {\bf\em Arabic Audio Book} - An audio pdf for learning Arabic. Pronunciation, pictures, and short sentences are used together to help understanding and memorizing each word. \href{http://bit.ly/28Qbqj2}{Download}.

% \end{rSubsection}

% \begin{rSubsection}{Course Projects}{}{}{}{}{}

% \item {\bf\em Single View Metrology} - Stereo from single image based on prior knowledge about few scene coordinates. \href{http://zhengrui.github.io/singleviewmetrology.html}{Blog Post}.

% \item {\bf\em Dense Light Stereo} - Stereo from massive images densely sampled with different light sources. \href{http://zhengrui.github.io/denselightstereo.html}{Blog Post}.

% \item {\bf\em Image Scissor} - Implement lasso function which most image editing tools have. \href{http://zhengrui.github.io/iscissor.html}{Blog Post}.

% \end{rSubsection}

% \end{rSection}


% \begin{rSection}{Miscellaneous}
% \begin{itemize}[label=\raisebox{0.25ex}{\tiny\JackStarBold}]
%     \item Language levels: native {\it Chinese}, full professional proficient {\it English}.
%     \item Course records: {\it Machine Learning} {\color{DarkOrchid} A}, {\it Computer Vision} {\color{DarkOrchid} A+}, {\it Bayesian Network} {\color{DarkOrchid} A-}, {\it Algorithm Design and Analysis} {\color{DarkOrchid} A}.
%     \item Hobbies: excellent at {\it table tennis} and {\it basketball}, good at {\it billiards}.
% \end{itemize}
% \end{rSection}

\end{document}
